\section{Introduction}
\label{sec:intro}

Magnetic fields are ubiquitous in the universe on all observed scales \cite{2013A&ARv..21...62D,Vallee04,Neronov10,2005LNP...664...89W,2012SSRv..166..215B}. However, the question of origins of the magnetic fields in galaxies and on large scales is as of yet unresolved. Various forms of dynamo mechanism have been proposed to maintain and amplify them \cite{2013PhRvE..87e3110P}, but they typically require the presence of seed fields \cite{2013A&ARv..21...62D}. Such seed fields may be produced during structure formation through the Biermann battery process or similar mechanisms \cite{Naoz13,2013PhRvL.111e1303N}, or may otherwise be relics from the early universe \cite{2013A&ARv..21...62D,2012SSRv..166...37W,2014JCAP...05..040K}. Observations of large--scale low--strength magnetic fields in the high--redshift intergalactic medium (IGM) could thus probe the origins of present--day magnetic fields and potentially open up an entirely new window into the physics of the early universe.

Many observational probes have been previously proposed and used to search for large--scale magnetic fields locally and at high redshifts (e.~g.~\cite{Yamazaki10,Blasi99,Tavecchio10,Dolag11,2005LNP...664...89W,2014JCAP...01..009K,2013ApJ...770...47K,2014PhRvD..89j3522S,2006MNRAS.372.1060T,2009ApJ...692..236S}). Amongst the most sensitive tracers of cosmological magnetic fields is the cumulative effect of Faraday rotation in the cosmic--microwave--background (CMB) polarization maps, which currently places an upper limit of $\sim$$10^{-10}$ Gauss (in comoving units) using data from the Planck satellite \cite{2015arXiv150201594P}. In Paper I of this series \cite{2014arXiv1410.2250V}, we proposed a novel method to detect and measure extremely weak cosmological magnetic fields during the pre--reionization epoch (the cosmic Dark Ages). This method relies on data from upcoming and future 21--cm tomography surveys \cite{1997ApJ...475..429M,2004PhRvL..92u1301L}, many of which have pathfinder experiments currently running \cite{2012arXiv1201.1700G,2011AAS...21813206B,2014ApJ...788..106P,2008arXiv0802.1727C,Vanderlinde14,2015AAS...22532803D}, with the next--stage experiments planned for the coming decade \cite{2008arXiv0802.1727C,2015AAS...22532803D}. 

In Paper I, we calculated the effect of a magnetic field on the observed 21--cm brightness--temperature fluctuations, and in this Paper, we focus on evaluating the sensitivity of future 21--cm experiments to measuring this effect. As we pointed out in Paper I, the 21--cm signal from the cosmic Dark Ages has an intrinsic sensitivity to capturing the effect of the magnetic fields in the IGM that are more than \textit{ten orders of magnitude smaller than the current upper limits on primordial magnetic fields from the CMB}. In the following, we demonstrate that a square--kilometer array of dipole antennas in a compact grid can reach the sensitivity necessary to detect large--scale magnetic fields that are on the order of $10^{-21}$ Gauss comoving (scaled to present day, assuming adiabatic evolution of the field due to Hubble expansion). 

The rest of this Paper is organized as follows. In \S\ref{sec:method}, we summarize the main results of Paper I. In \S\ref{sec:basics}, we define our notation and review the basics of the 21--cm signal and its measurement. In \S\ref{sec:estimators}, we derive minimum--variance estimators for uniform and stochastic magnetic fields. In \S\ref{sec:fisher}, we set up the Fisher formalism necessary to forecast sensitivity of future surveys. In \S\ref{sec:results}, we present our sensitivity forecasts. In \S\ref{sec:conclusions} we summarize and discuss the implications of our results. Supporting materials are presented in the appendices.